{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}

### 2024-08-05 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, some changes and updates to the notebooks

            \begin{definition}[AG Proximal Gradient Tri-Points Generic Form]
            \label{def:ag_prox_grad_tri_pt}
                With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
                Define proximal gradient and gradient mapping operator 
                $$
                \begin{aligned}
                    \mathcal T_L(x) 
                    &:= \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)), 
                    \\
                    x^+ &= \mathcal T_L(x), 
                    \\
                    \mathcal G_L(x) 
                    &:= L(x -  x^+). 
                \end{aligned}
                $$
                Then the algorithm updates $(y_t, x_{t + 1}, z_{t + 1})$ with expression: 
                $$
                \begin{aligned}
                    y_t^+ &= \mathcal T_L(y_t)
                    \\
                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
                    \\
                    x_{t + 1} &= x_t - \tilde \eta \mathcal G_L(y_t)
                    \\
                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
                \end{aligned}
                $$
                for all $t\in \mathbb N$ where the base case has $y_0 = x_0$. 
            \end{definition}
            \begin{remark}
                Observe that $z_{t + 1} = y_t^+$. 
            \end{remark}

            \begin{definition}[Tri-points Generic Form]\label{def:agg_tri}
                With $f$ be $L$-Lipschitz \\ 
                smooth and convex, choose any $y_0 = x_0=z_0$ and a non-negative sequence $\eta_t, \tilde\eta_t$, the algorithm admits form: 
                \begin{align*}
                    x_{t + 1} &= x_t - \tilde \eta_{t + 1} \nabla f(y_t) 
                    \\
                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
                    \\
                    y_{t + 1} &= 
                    (1 + L\eta_{t + 1})^{-1}
                    (
                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
                    ). 
                \end{align*}
            \end{definition}
            \begin{remark}
                The parameter $\eta_t, \tilde\eta_{t + 1}$ are exactly the same as Ahn, Sra \cite[(6.24)]{ahn_understanding_2022}, but with the choice of $\mu = 0$. 
                This form is not explictly stated by Ahn and Sra but it's trivial to realize its presence regardless. 
                They are the same parameters for both algorithms and they are equivalent. 
                For a demonstration, see 
                \hyperref[prop:tri_form_via_ppm]{proposition \ref*{prop:tri_form_via_ppm}}. 
            \end{remark}

            \begin{definition}[Strongly Convex Tri-points Generic Form]
                \quad \\
                With $f$ being $L$-Lipschitz smooth and $\mu > 0$ strongly convex then the Strongly convex Tri-Points generic form has updates of for iterates
                \begin{align*}
                    x_{t + 1} &= (1 + \mu\tilde \eta_{t + 1})^{-1}(x_t + \mu\tilde\eta_{t + 1}y_t^+), 
                    \\
                    z_{t + 1} &= y_t - L^{-1}\nabla f(y_t), 
                    \\
                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L\eta_{t + 1}z_{t +1}). 
                \end{align*}
            \end{definition}
            \begin{remark}
                This algorithm is equivalent to 
                \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}. 
                See \ref*{prop:tri_scvx_from_ahn_sra_6.24} for a demonstration. 
            \end{remark}

@@

            \begin{lemma}[Similar Triangle Form I via Generic Tri Points]

@@

                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L f(y_t)

>>>>

            \begin{definition}[AG Proximal Gradient Generic Form]
            \label{def:ag_prox_grad_tri_pt}
                With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
                Define proximal gradient and gradient mapping operator 
                $$
                \begin{aligned}
                    \mathcal T_L(x) 
                    &:= \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)), 
                    \\
                    x^+ &= \mathcal T_L(x), 
                    \\
                    \mathcal G_L(x) 
                    &:= L(x -  x^+). 
                \end{aligned}
                $$
                Then the algorithm updates $(y_t, x_{t + 1}, z_{t + 1})$ with expression: 
                $$
                \begin{aligned}
                    y_t^+ &= \mathcal T_L(y_t)
                    \\
                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
                    \\
                    x_{t + 1} &= x_t - \tilde \eta \mathcal G_L(y_t)
                    \\
                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
                \end{aligned}
                $$
                for all $t\in \mathbb N$ where the base case has $y_0 = x_0$. 
            \end{definition}
            \begin{remark}
                Observe that $z_{t + 1} = y_t^+$. 
            \end{remark}

            \begin{definition}[Generic Form]\label{def:agg_tri}
                With $f$ be $L$-Lipschitz \\ 
                smooth and convex, choose any $y_0 = x_0=z_0$ and a non-negative sequence $\eta_t, \tilde\eta_t$, the algorithm admits form: 
                \begin{align*}
                    x_{t + 1} &= x_t - \tilde \eta_{t + 1} \nabla f(y_t) 
                    \\
                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
                    \\
                    y_{t + 1} &= 
                    (1 + L\eta_{t + 1})^{-1}
                    (
                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
                    ). 
                \end{align*}
            \end{definition}
            \begin{remark}
                The parameter $\eta_t, \tilde\eta_{t + 1}$ are exactly the same as Ahn, Sra \cite[(6.24)]{ahn_understanding_2022}, but with the choice of $\mu = 0$. 
                This form is not explictly stated by Ahn and Sra but it's trivial to realize its presence regardless. 
                They are the same parameters for both algorithms and they are equivalent. 
                For a demonstration, see 
                \hyperref[prop:tri_form_via_ppm]{proposition \ref*{prop:tri_form_via_ppm}}. 
            \end{remark}

            \begin{definition}[Strongly Convex Generic Form]
                \quad \\
                With $f$ being $L$-Lipschitz smooth and $\mu > 0$ strongly convex then the Strongly convex generic form has updates of for iterates
                \begin{align*}
                    x_{t + 1} &= (1 + \mu\tilde \eta_{t + 1})^{-1}(x_t + \mu\tilde\eta_{t + 1}y_t^+), 
                    \\
                    z_{t + 1} &= y_t - L^{-1}\nabla f(y_t), 
                    \\
                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L\eta_{t + 1}z_{t +1}). 
                \end{align*}
            \end{definition}
            \begin{remark}
                This algorithm is equivalent to 
                \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}. 
                See \ref*{prop:tri_scvx_from_ahn_sra_6.24} for a demonstration. 
            \end{remark}

@@

            \begin{lemma}[Deriving Similar Triangle Form I]

@@

                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L (y_t)
